Paper Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-03-25 Initial-paper/paper.tex
added important papers and changes paper setup
Write down the goal of the paper what we want to claim/show

\begin{abstract}
blabla
\end{abstract}

@@

\begin{itemize}
	\item Describe domains from IPPC
	\item Explain shortcomings
	\item Evaluate a valuable real-world domain in which we can test 2 papers
\end{itemize}

>>>>

\begin{abstract}
	This paper argues that for many real life domains dead-ends are the end of
	the world, and by for example human interaction the goal can still be
	reached. By relaxing the definition of a dead-end, we argue that for many
	real life domains a simpler planning algorithm, like FF-Replan, can be
	sufficient, and that it's not needed to have newer and sophisticated
	probabilistic planners.
\end{abstract}

@@

\begin{itemize}
	\item Describe domains from IPPC
	\item Explain shortcomings
	\item Evaluate a valuable real-world domain in which we can test 2 papers
	\item Show PPDDL or RDDL of domain (probabilistic extension of PDDL)
\end{itemize}
